ISYE 6501

### 2022-09-14 hw3-1/submission.Rmd
draft v2

```{r}

```

>>>>

We can further test this hypothesis by looking at average temperatures of different months in the same windows.

```{r}
aggregate_on_month_and_transpose = function(df, func){
  return_df = aggregate(. ~ month, df, func)
  n = return_df$month
  # transpose all but the first column (month)
  return_df <- as.data.frame(t(return_df[,-1]))
  colnames(return_df) <- n
  return_df = cbind(Year = rownames(return_df), return_df)
  rownames(return_df) = 1:nrow(return_df)
  return_df = return_df[, c(1, 3, 2, 5, 4)]
  return_df
}

month_df = data_celsius[,!(names(data_celsius) %in% c("DAY"))]
for ( col in 1:ncol(month_df)){
    colnames(month_df)[col] <-  sub("X", "", colnames(month_df)[col])
}

year_bucketing_function = function(df){
  df["year_bucket"] = "a.1996_2000"
  df[df$Year>=2000,"year_bucket"] = "b.2000_2004"
  df[df$Year>=2004,"year_bucket"] = "c.2004_2008"
  df[df$Year>=2008,"year_bucket"] = "d.2008_2012"
  df[df$Year>=2012,"year_bucket"] = "e.2012_2016"
  df
}
```

#### Mean of Average temperature (daily high)

```{r}
mean_df = aggregate_on_month_and_transpose(month_df, mean)
mean_df = year_bucketing_function(mean_df)
mean_df = mean_df[,-1]
mean_df = aggregate(.~year_bucket, mean_df, mean)
mean_df
```

#### Mean of Min temperature

```{r}
min_df = aggregate_on_month_and_transpose(month_df, min)
min_df = year_bucketing_function(min_df)
min_df = min_df[,-1]
min_df = aggregate(.~year_bucket, min_df, mean)
min_df
```

#### Mean of Max temperature

```{r}
max_df = aggregate_on_month_and_transpose(month_df, max)
max_df = year_bucketing_function(max_df)
max_df = max_df[,-1]
max_df = aggregate(.~year_bucket, max_df, mean)
max_df
```
